Fig3

### 2020-03-27 analysis/figure-3.Rmd
better caption, better size

@@

```{r fig3, fig.width=7, fig.height=7}
makeboxplots <- function(df, whichgene, mysubtitle, whichsex, whichtimepoint){
  p <- df %>%
    filter(treatment %in% charlevels,
           gene %in% whichgene,
           sex %in% whichsex) %>%
    filter(treatment %in% whichtimepoint) %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) + 
    geom_jitter(size = 0.5, width = 0.1) +
    facet_wrap(~gene, scales = "free_y", nrow = 1) +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    labs(y = "expression" , x = "Parental stages", subtitle = mysubtitle) +
    theme(strip.text = element_text(face = "italic"))
  return(p)
}

@@

@@

cde <- plot_grid(c,d, e, rel_widths = c(2.5,2.5,1), nrow = 1)

g <- makeboxplots(gonvsd, c( "AVPR1A"), "Female gonads", "female", c( "lay", "inc.d3", "inc.d9"))  +
  theme(axis.title.x = element_blank())
h <- makeboxplots(gonvsd, c( "EGR1", "FOS", "PRLR"), " ", "female", c( "lay", "inc.d3"))  +
  theme(axis.title = element_blank())

gh <- plot_grid(g,h,nrow = 1, rel_widths = c(1,2.5))

b <- makeboxplots(hypvsd, c("AR"),"Male hypothalamic expression", "male", 
                  c( "inc.d9", "inc.d17"))  + labs(caption = " ")
f <- makeboxplots(pitvsd, c("LBH", "PRL"), "Male pituitary expression", "male", 
                  c("inc.d9", "inc.d17")) + 
  theme(axis.title.y  = element_blank(),
        plot.caption = element_text(face = "italic")) + 
  labs(caption = "candidate genes: AR, AVP, AVPR1A, AVPR1B, AVPR2, BDNF, CYP19A1, DRD1, EGR1, ESR1, ESR2, FOS, GNRH1, GNRHR, JUN, LBH, OXT, PRL, PRLR, VIP")

bf <- plot_grid(b,f,nrow = 1, rel_widths = c(1,2))

plot_grid(a, cde, gh, bf, nrow = 4, rel_heights = c(1,1,1,1.2), labels = "auto", label_size = 8)

>>>>

# all candidate genes: AR, AVP, AVPR1A, AVPR1B, AVPR2, BDNF, CYP19A1, DRD1, EGR1, ESR1, ESR2, FOS, GNRH1, GNRHR, JUN, LBH, OXT, PRL, PRLR, VIP

# DEG candidate genes: AR, AVPR1A, AVPR1B, AVPR2, BDNF, CYP19A1, DRD1, ESR1, FOS, GNRHR, LBH, PRL, PRLR,

# Candidate genes that were not differentially expressed: AVP, AVPR1B, ESR2,  GNRH1, JUN, OXT, VIP

@@

```{r fig3, fig.width=7, fig.height=7}
makeboxplots <- function(df, whichgene, mysubtitle, whichsex, whichtimepoint){
  p <- df %>%
    filter(treatment %in% charlevels,
           gene %in% whichgene,
           sex %in% whichsex) %>%
    filter(treatment %in% whichtimepoint) %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) + 
    geom_jitter(size = 0.5, width = 0.1) +
    facet_wrap(~gene, scales = "free_y", nrow = 1) +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(#axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    labs(y = "gene expression" , x = "Sequential stages with candidate DEGs", subtitle = mysubtitle) +
    theme(strip.text = element_text(face = "italic"))
  return(p)
}

@@

b <- makeboxplots(hypvsd, c("AR"),"Male hypothalamus", "male", 
                  c( "inc.d9", "inc.d17"))  +
  theme(axis.title = element_blank())

ab <- plot_grid(a,b, rel_widths = c(4,1),  labels = "auto", label_size = 8)

@@

cde <- plot_grid(c,e,d, rel_widths = c(6,2.25,7), nrow = 1,  labels = c("c"), label_size = 8)

g <- makeboxplots(gonvsd, c( "AVPR1A"), "Female gonads", "female", c( "lay", "inc.d3", "inc.d9"))  +
  labs(caption = " ", x = " ")
h <- makeboxplots(gonvsd, c( "EGR1", "FOS", "PRLR"), " ", "female", c( "lay", "inc.d3"))  +
  theme(axis.title.y = element_blank()) + labs(caption = " ")
f <- makeboxplots(pitvsd, c("LBH", "PRL"), "Male pituitary", "male", 
                  c("inc.d9", "inc.d17")) + 
  theme(plot.caption = element_text(face = "italic")) + 
  labs(x = " ",
       caption = "Candidate genes that were not differentially expressed from bldg to n5: AVP, AVPR1B, ESR2,  GNRH1, JUN, OXT, VIP.")

ghf <- plot_grid(g,h,f, nrow = 1, rel_widths = c(3,6,4),  labels = c("d", " ", "e"), label_size = 8)

plot_grid(ab, cde, ghf, nrow = 3, rel_heights = c(1,1,1.25))
